Setup Honeypot: Team Contagiarium

### 2011-11-01 Setup_honeypot.tex
extended some text

\subsection{Setup: Honeypot}

More text.

>>>>

\subsection{Root}

\section{Setup: Honeypot}

In this section we decribe the setup of the honeypot.

\subsection{scanlogd}

To detect portscans we have installed the tool scanlogd.
Per scan an entry is written to syslog.

\subsection{iptables}
To log all connection attempts coming in and going out, we have added the following rules to the iptables configuration. 
This will also log to syslog.

\emph{iptables -I INPUT -m state --state NEW -j LOG --log-prefix "New Connection: "}

\emph{iptables -I OUTPUT -m state --state NEW -j LOG --log-prefix "New Connection: "}

\subsection{Kippo}
To capture attackers that try to come in over ssh, we are using Kippo. 
Kippo is used to log bruteforce attacks and the shell interaction performed by the attacker. 
To make this as realistic as possible we have added a redicrect in the iptables configuration from port 22 to port 2222 that kippo uses. 
Unfortunately this broke down after a while, for reasons yet unknown. 
The reason for forwarding was not to give Kippo root capabilities.

To be able to still log on to the honeypot, we configured port 9022 to be used by ssh.

\subsection{Google Hack Honeypot}
Google Hack Honeypot (GHH) is used to attract search engine attackers. 
These attackers will use search queries to find sensitive data, for example password files, that due to some misconfiguration ended up being indexed by a search engine like google.
To set this up we have first installed Apache and PHP5.
Then we configured GHH to use Comma Seperated Values, since MySQL was not installed yet on the util machine and to see if this would actually work. 
We can later reconfigure to use MySQL, if the results are not satisfactory.
Since GHH offers multiple setup honeypot we picked one to start with, namely GGH version 1.2 passlist.txt.
We had no particular reason for this, only that it was easy to set up. 
The plan was to install more variants of the GHH to attract more attackers, but before this could happen the VM's were shut down.

\subsection{Snort}

Stukje Joost en Bart.
